### 2016-04-27 thesis/declaration.tex
copyright no
dispatched

I warrant that I have obtained, where necessary, permission from the copyright owners to use 
any third part copyright material reproduced in the thesis, 
or to use any of my own published work in which the copyright 
is held by another party.

>>>>

I warrant that I have obtained, where necessary, permission from the copyright owners to use 
any third part copyright material reproduced in the thesis, 
or to use any of my own published work in which the copyright 
is held by another party. 
AAS and Oxford University Press grant back to authors the non-exclusive right of republication, 
subject only to giving appropriate credit to the journal in which the article was published. 
This non-exclusive right of republication gives authors the right to approve or deny 
reproduction of all or part of the article and to post the final published version online.  
No written permission is required to have the papers reproduced in the thesis with the original journal 
format\footnote{For more information, see 
\url{http://iopscience.iop.org/page/copyright} and 
\url{http://www.oxfordjournals.org/our_journals/mnras/rights_permissions_ras.html} .}.
